Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-06-08 paper/paper.tex
Difference between branching and filtering

Finally, the two approaches for ensuring connectedness (branching and filtering) are complementary
and may be combined: at each step of the search, we select the next variable to be assigned within
the neighbors of $A$, and each time a vertex of $H$ is removed from a domain we filter
domains to ensure connectedness consistency.

>>>>

Finally, the two approaches for ensuring connectedness (branching and filtering) are complementary
and may be combined: at each step of the search, we select the next variable to be assigned within
the neighbors of $A$, and each time a vertex of $H$ is removed from a domain we filter domains to
ensure connectedness consistency. In the example in \cref{figure:restricted}, after the first
assignment, filtering alone would remove $5$ from every domain but would allow branching on any
remaining variable, whilst branching alone would force the next variable to be either $b$ or $c$ but
would not immediately eliminate $5$ from the domains of $d$ and $e$.
